Long-form recording of infant body position in the home using wearable inertial sensors

### 2023-06-20 manuscript.Rmd
cutting

From moment to moment, infants' movements facilitate and constrain how they can interact with their surroundings. Changes in *body position*---whether infants are supine on their backs, prone on their bellies, sitting, upright, or held by a caregiver---have immediate consequences for vision, object exploration, and social interaction. When sitting and upright, infants have a better view of faces and distant objects compared to their view while in a prone position [@Freeplay; @LuoFranchak2020; @CWW]. Learning to sit facilitates object exploration [@SoskaAdolph2014]. Upright walking changes how infants and caregivers interact; walking infants move farther away from caregivers and share toys in different ways compared to infants crawling in a prone position [@ChenSchneider2022; @Karasik2011]. As infants grow older and acquire new abilities, such as independent sitting and walking, they spend more time sitting and upright and less time held, supine, and prone [@Survey; @Thurman2017; @Freeplay; @AdolphCTL2014]. Caregivers provide different learning input to infants depending on infants' body position [@KretchKoziol2022; @WestIverson2021; @Karasik2014]. For example, infants' walking movements spur caregivers to talk about actions rather than just describe objects. Thus, characterizing individual differences in the day-to-day accumulation of body position experiences informs developmental theory by revealing differential opportunities for learning [@CurrentOpinion].

In this paper, we present an inertial sensing method to classify infant body position from moment to moment across an entire day, and validate its accuracy using over 100 hours of video recorded across 34 in-home data collection sessions. Our method takes inspiration from a more mature technology: Long-form audio recordings of infants' language experiences using wearable audio recorders. We begin by describing the impact of long-form audio recordings on research in developmental psychology, and identify the key features that should be replicated in long-form recordings of motor behavior. Next, we review the current state-of-the-art in measuring infant motor behavior---video and survey data---and their limitations in capturing real-time, full-day behavior. Finally, we discuss the advantages of using inertial sensing to classify motor behavior. Despite promising past results in brief, supervised sessions [@FranchakScott2021; @AiraksinenRasanen2020; @AiraksinenGallen2022], the current investigation takes a needed step forward by testing accuracy over long, unsupervised recordings in what we term a *distal comparison*.

@@

The LENA&reg; recorder is a commercial device worn in a custom shirt pocket; the recorder has sufficient battery life and storage to record for an entire day. Closed-source LENA&reg; algorithms analyze the audio recordings to provide automatic counts of useful metrics, such as the number of words spoken by adults in the vicinity of the infant. Other long-form audio methods rely on custom-built recorders [@WassPhillips2022], apply alternative classification algorithms to LENA&reg; data [@RasanenSeshadri2020; @MichelettiYao2022], or manually transcribe audio recorded by LENA&reg; devices to improve accuracy or identify behaviors beyond the built-in categories [@Bergelson2019Corpus; @MendozaFausey2021].

Long-form audio recordings have had a transformational impact on language development research by allowing researchers to characterize opportunities for learning in daily life. For example, measuring the amount of speech heard by infants in the home [@Weisleder2013] or in a daycare setting [@PerryPrince2018] revealed how individual differences in speech input predict later vocabulary. Full-day language recording synchronized with other data sources allows researchers to identify how auditory input and vocal production interact with other processes. Beyond individual differences in aggregated data, long-form recordings reveal the temporal schedule of experiences. For example, infants' daily experiences hearing music are clustered in time, with "bursty" episodes of music presence separated by relatively long periods during which music is absent [@MendozaFausey2022]. In addition, synchronizing audio recordings with other data sources extends researchers' ability to characterize daily experiences. Linking LENA&reg; speech measurements to repeated, time-stamped text-message surveys about infant device placement revealed that infants heard less caregiver speech during periods that they were restrained in devices such as swings, exersaucers, and car seats [@MalachowskiSalo2023]. A custom-built wearable ECG and audio recorder allowed @WassPhillips2022 to discover that infant arousal increases the likelihood of infant vocalization across the day.

We identified five key features of long-form audio methods that should be replicated in analogous studies of motor behavior. First, wearable audio recorders are *mobile*. Measurement is not limited to a particular room because the recording device travels with the participant. Data are recorded to onboard device memory, so participants do not need to be in range of a receiver. Second, wearable audio recording is more *unobtrusive*. Participants' reactivity to observation, such as from a video camera, may influence behavior more compared with a sensor that records only motion or audio data. For example, caregivers spoke more frequently to infants during a video-recorded portion of a home recording compared with audio-only segments captured by a LENA&reg; device [@Bergelson2019Input]. Third and fourth, recordings capture *real-time data* over a *full day*. The ability to record real-time data is vital for making inferences about processes that happen on the timescale of minutes or even seconds within an individual as opposed to comparisons of aggregated data between infants. Synchronizing real-time data to other data streams helps to reveal sources of variability within an individual [e.g., @WassPhillips2022; @MalachowskiSalo2023]. Full-day recordings are essential for capturing experiences across the heterogeneity of daily routines that moderate behavior (e.g., play, feeding, errands) [@KadookaCaufield2021; @Tamis-LeMondaCustode2018]. "Burstiness" of behavior means that long recordings are needed to capture clusters of events amid long periods in which they may be absent [@BarbaroFausey2022; @WarlaumontSobowale2021]. Fifth, *automatic classification* means that the approach can scale to analyze large numbers of participants over long recordings without the bottleneck of manual annotation/transcription.

But automatic classification can only replace human annotation if it is sufficiently accurate and unbiased. An independent assessment of the LENA&reg; algorithms found mixed results about the accuracy of different measurements. For example, correlations between human transcribed counts of adult words and child vocalizations against LENA&reg;'s automatic counts were strong, *r* = .698 and *r* = .649, respectively [@CristiaLavechin2020]. For other metrics, such as the number of "conversational turns" between the child and communicative partners, agreement was poor (*r* = .364). Thus, for some use cases (and for some metrics), long form audio recordings provide a mobile, unobtrusive way to automatically score real-time data over a full day. In the remainder of the paper, we turn to the question of how to replicate those key features in long form recordings of motor behavior.

@@

Video and survey methods are the current state-of-the-art in assessing infants' gross motor behavior in naturalistic tasks. Although each method has complementary advantages and disadvantages for characterizing infants' everyday motor experiences, neither method on its own can provide comparable data to the long form audio recordings reviewed in the previous section.

Video observation is the most common way of measuring infant motor behavior in home recordings. Most often, an experimenter with a handheld camera follows infants from room to room to ensure that their movements are visible throughout the recording session [@Karasik2011; @ChenSchneider2022; @HerzbergFletcher2021]. The primary advantage of video recording is that it captures real-time behavior. Infants' body position, locomotion, and reaching comprise events that occur on the timescale of seconds, so standard video recording is adequate to score gross motor behavior. However, requiring an experimenter to operate a camera is obtrusive, whereas relying on a stationary camera means that infants will be absent from view as they move from place to place. Moreover, video observation cannot easily scale to long durations or large numbers of participants. Logistically, an experimenter cannot follow behind infants to record their behavior from morning to night (and were they to do so, they would likely alter infants' and caregivers' behavior). Typical video recording sessions last 45-120 minutes [@Karasik2011; @ChenSchneider2022; @HerzbergFletcher2021], far short of capturing the variety of activities across the full daily routine. Even if full day videos were available, the lack of suitable automatic classification tools means that the human cost of annotation makes it difficult for video methods to scale to testing large numbers of participants. Our annotation of body position takes approximately 2-5 hours to complete for every hour of video (depending on how often infants switch positions), meaning that a full "waking day" of approximately 11 hours for a 12-month-old [@GallandTaylor2012] could take 22-55 hours of labor to fully annotate.

In contrast, survey methods such as daily diaries/inventories or ecological momentary assessment (EMA) are mobile, unobtrusive, can be applied across an entire day, and do not need laborious annotation. Diary studies provide caregivers with logs or structured interviews to estimate from memory how much time infants spend in particular activities [@MajnemerBarr2005; @KarasikKuchirko2022]. Ecological momentary assessment uses text-message or app-based notifications to prompt caregivers to make repeated estimates of infants' behavior over the course of a day [@Survey; @KadookaCaufield2021]. Although the EMA responses are valuable in aggregate, survey methods lack the real-time temporal resolution to describe moment-to-moment changes in behavior. For diaries and interviews, limits on caregivers' memory mean that they will report what was most frequent, but cannot remember events that happen on the scale of seconds and minutes. At best, EMA surveys prompt caregivers to make hourly observations; increasing the number of surveys per day would be too burdensome for the respondent. Thus, despite being a useful tool for estimating broad developmental changes and individual differences in infants' motor experiences, survey methods are not suited for capturing within-participant temporal dynamics.

>>>>

Infants' movements facilitate and constrain how they can interact with their surroundings. Changes in *body position*---whether infants are supine on their backs, prone on their bellies, sitting, upright, or held by a caregiver---have in-the-moment consequences for vision, object exploration, and social interaction. When sitting and upright, infants have a better view of faces and distant objects compared to their view while prone [@Freeplay; @LuoFranchak2020; @CWW]. While walking upright, infants move farther away from caregivers and share toys in different ways compared to infants crawling in a prone position [@ChenSchneider2022; @Karasik2011]. As infants grow older and acquire new abilities, such as independent sitting and walking, they spend more time sitting and upright and less time held, supine, and prone [@Survey; @Thurman2017; @Freeplay; @AdolphCTL2014]. Thus, characterizing individual differences in the day-to-day accumulation of body position experiences informs developmental theory by revealing differential opportunities for learning [@CurrentOpinion].

In this paper, we present an inertial sensing method to classify infants' full-day, real-time body position. Our method takes inspiration from a more mature technology: Long-form audio recordings of infants' language experiences. We begin by identifying the key features of wearable audio recorders that should be replicated in long-form recordings of motor behavior. Next, we review the current state-of-the-art in measuring infant motor behavior---video and survey data---and their limitations in capturing real-time, full-day behavior. Finally, we discuss the advantages of using inertial sensing to classify motor behavior. Despite promising past results in brief, supervised sessions [@FranchakScott2021; @AiraksinenRasanen2020; @AiraksinenGallen2022], the current investigation takes a needed step forward by testing accuracy over long, unsupervised recordings in what we term a *distal comparison*.

@@

The LENA&reg; recorder is a commercial device worn in a custom shirt pocket; the recorder has sufficient battery life and storage to record for an entire day. Closed-source LENA&reg; algorithms analyze the audio recordings to provide automatic counts of useful metrics, such as the number of words spoken by adults in the vicinity of the infant. Long-form audio recordings have had a transformational impact on language development research by allowing researchers to characterize opportunities for learning in daily life. For example, measuring the amount of speech heard by infants in the home [@Weisleder2013] or in a daycare setting [@PerryPrince2018] revealed how individual differences in speech input predict later vocabulary. Full-day language recording synchronized with other data sources allows researchers to identify how auditory input and vocal production interact with other processes. Beyond individual differences in aggregated data, long-form recordings reveal the temporal schedule of experiences. For example, infants' daily experiences hearing music are clustered in time, with "bursty" episodes of music presence separated by relatively long periods during which music is absent [@MendozaFausey2022].

We identified five key features of long-form audio methods that should be replicated in analogous studies of motor behavior. First, wearable audio recorders are *mobile*. Measurement is not limited to a particular room because the recording device travels with the participant. Data are recorded to onboard device memory, so participants do not need to be in range of a receiver. Second, wearable audio recording is more *unobtrusive*. Participants' reactivity to observation, such as from a video camera, may influence behavior more compared with a sensor that records only motion or audio data. For example, caregivers spoke more frequently to infants during a video-recorded portion of a home recording compared with audio-only segments captured by a LENA&reg; device [@Bergelson2019Input]. Third and fourth, recordings capture *real-time data* over a *full day*. Real-time data are vital for identifying processes that unfold over minutes or seconds within an individual as opposed to comparisons of aggregated data between infants. Synchronizing real-time data to other data streams helps to reveal sources of variability within an individual [e.g., @WassPhillips2022; @MalachowskiSalo2023]. Full-day recordings are essential for capturing experiences across the heterogeneity of daily routines that moderate behavior (e.g., play, feeding, errands) [@KadookaCaufield2021; @Tamis-LeMondaCustode2018]. "Burstiness" of behavior means that long recordings are needed to capture clusters of events amid long periods in which they may be absent [@BarbaroFausey2022; @WarlaumontSobowale2021]. Fifth, *automatic classification* means that the approach can scale to analyze large numbers of participants over long recordings without the bottleneck of manual annotation/transcription.

But automatic classification can only replace human annotation if it is sufficiently accurate. An independent assessment of the LENA&reg; algorithms found mixed results about classification accuracy. Correlations between human transcribed counts of adult words and child vocalizations against LENA&reg;'s automatic counts were strong, *r* = .698 and *r* = .649, respectively [@CristiaLavechin2020]. For other metrics, such as the number of "conversational turns" between the child and communicative partners, agreement was poor (*r* = .364). Thus, for some use cases (and for some metrics), long form audio recordings provide a mobile, unobtrusive way to automatically score real-time data over a full day. 
<!-- In the remainder of the paper, we turn to the question of how to replicate those key features in long form recordings of motor behavior. -->

@@

Video and survey methods are the current state-of-the-art in assessing infants' gross motor behavior in naturalistic tasks. Although each method has complementary advantages and disadvantages for characterizing infants' everyday motor experiences, neither method fulfills all five key features of long form audio recordings reviewed in the previous section.

Video observation is the most common way of measuring infant motor behavior in home recordings. Most often, an experimenter with a handheld camera follows infants from room to room to ensure that their movements are visible throughout the recording session [@Karasik2011; @ChenSchneider2022; @HerzbergFletcher2021]. The primary advantage of video recording is that it captures real-time behavior.Standard 30 Hz video recording is adequate to capture changes in infant body position that occur on the timescale of seconds. However, requiring an experimenter to operate a camera is obtrusive, whereas relying on a stationary camera means that infants will be absent from view as they move from place to place. Moreover, video observation cannot easily scale to long durations or large numbers of participants. An experimenter cannot follow behind infants to record their behavior from morning to night; typical video recording sessions last 45-120 minutes [@Karasik2011; @ChenSchneider2022; @HerzbergFletcher2021], far short of capturing the variety of activities across the full daily routine. Even if full-day videos were available, the lack of suitable automatic classification tools means that the human cost of annotation would be immense. Our annotation of body position takes approximately 2-5 hours to complete for every hour of video (depending on how often infants switch positions), meaning that a full "waking day" of approximately 11 hours for a 12-month-old [@GallandTaylor2012] could take 22-55 hours of labor to annotate.

In contrast, survey methods such as daily diaries/inventories or ecological momentary assessment (EMA) are mobile, unobtrusive, can be applied across an entire day, and do not need laborious annotation. Diary studies provide caregivers with logs or structured interviews record activities [@MajnemerBarr2005; @KarasikKuchirko2022]. Ecological momentary assessment uses smartphone notifications to prompt caregivers to make repeated estimates of behaviors throughout the day [@Survey; @KadookaCaufield2021]. Although such survey responses are valuable in aggregate, they  lack the real-time temporal resolution to describe moment-to-moment changes in behavior. At best, EMA surveys prompt caregivers to make hourly observations; increasing the number of surveys per day would be too burdensome for the respondent. Thus, despite being a useful tool for estimating broad developmental changes and individual differences in infants' motor experiences, survey methods are not suited for capturing within-participant temporal dynamics.

### 2023-06-20 manuscript.tex
cutting

From moment to moment, infants' movements facilitate and constrain how they can interact with their surroundings. Changes in \emph{body position}---whether infants are supine on their backs, prone on their bellies, sitting, upright, or held by a caregiver---have immediate consequences for vision, object exploration, and social interaction. When sitting and upright, infants have a better view of faces and distant objects compared to their view while in a prone position \autocite{Freeplay,LuoFranchak2020,CWW}. Learning to sit facilitates object exploration \autocite{SoskaAdolph2014}. Upright walking changes how infants and caregivers interact; walking infants move farther away from caregivers and share toys in different ways compared to infants crawling in a prone position \autocite{ChenSchneider2022,Karasik2011}. As infants grow older and acquire new abilities, such as independent sitting and walking, they spend more time sitting and upright and less time held, supine, and prone \autocite{Survey,Thurman2017,Freeplay,AdolphCTL2014}. Caregivers provide different learning input to infants depending on infants' body position \autocite{KretchKoziol2022,WestIverson2021,Karasik2014}. For example, infants' walking movements spur caregivers to talk about actions rather than just describe objects. Thus, characterizing individual differences in the day-to-day accumulation of body position experiences informs developmental theory by revealing differential opportunities for learning \autocite{CurrentOpinion}.

In this paper, we present an inertial sensing method to classify infant body position from moment to moment across an entire day, and validate its accuracy using over 100 hours of video recorded across 34 in-home data collection sessions. Our method takes inspiration from a more mature technology: Long-form audio recordings of infants' language experiences using wearable audio recorders. We begin by describing the impact of long-form audio recordings on research in developmental psychology, and identify the key features that should be replicated in long-form recordings of motor behavior. Next, we review the current state-of-the-art in measuring infant motor behavior---video and survey data---and their limitations in capturing real-time, full-day behavior. Finally, we discuss the advantages of using inertial sensing to classify motor behavior. Despite promising past results in brief, supervised sessions \autocite{FranchakScott2021,AiraksinenRasanen2020,AiraksinenGallen2022}, the current investigation takes a needed step forward by testing accuracy over long, unsupervised recordings in what we term a \emph{distal comparison}.

@@

The LENA® recorder is a commercial device worn in a custom shirt pocket; the recorder has sufficient battery life and storage to record for an entire day. Closed-source LENA® algorithms analyze the audio recordings to provide automatic counts of useful metrics, such as the number of words spoken by adults in the vicinity of the infant. Other long-form audio methods rely on custom-built recorders \autocite{WassPhillips2022}, apply alternative classification algorithms to LENA® data \autocite{RasanenSeshadri2020,MichelettiYao2022}, or manually transcribe audio recorded by LENA® devices to improve accuracy or identify behaviors beyond the built-in categories \autocite{Bergelson2019Corpus,MendozaFausey2021}.

Long-form audio recordings have had a transformational impact on language development research by allowing researchers to characterize opportunities for learning in daily life. For example, measuring the amount of speech heard by infants in the home \autocite{Weisleder2013} or in a daycare setting \autocite{PerryPrince2018} revealed how individual differences in speech input predict later vocabulary. Full-day language recording synchronized with other data sources allows researchers to identify how auditory input and vocal production interact with other processes. Beyond individual differences in aggregated data, long-form recordings reveal the temporal schedule of experiences. For example, infants' daily experiences hearing music are clustered in time, with ``bursty'' episodes of music presence separated by relatively long periods during which music is absent \autocite{MendozaFausey2022}. In addition, synchronizing audio recordings with other data sources extends researchers' ability to characterize daily experiences. Linking LENA® speech measurements to repeated, time-stamped text-message surveys about infant device placement revealed that infants heard less caregiver speech during periods that they were restrained in devices such as swings, exersaucers, and car seats \autocite{MalachowskiSalo2023}. A custom-built wearable ECG and audio recorder allowed \textcite{WassPhillips2022} to discover that infant arousal increases the likelihood of infant vocalization across the day.

We identified five key features of long-form audio methods that should be replicated in analogous studies of motor behavior. First, wearable audio recorders are \emph{mobile}. Measurement is not limited to a particular room because the recording device travels with the participant. Data are recorded to onboard device memory, so participants do not need to be in range of a receiver. Second, wearable audio recording is more \emph{unobtrusive}. Participants' reactivity to observation, such as from a video camera, may influence behavior more compared with a sensor that records only motion or audio data. For example, caregivers spoke more frequently to infants during a video-recorded portion of a home recording compared with audio-only segments captured by a LENA® device \autocite{Bergelson2019Input}. Third and fourth, recordings capture \emph{real-time data} over a \emph{full day}. The ability to record real-time data is vital for making inferences about processes that happen on the timescale of minutes or even seconds within an individual as opposed to comparisons of aggregated data between infants. Synchronizing real-time data to other data streams helps to reveal sources of variability within an individual \autocites[e.g.,][]{WassPhillips2022,MalachowskiSalo2023}. Full-day recordings are essential for capturing experiences across the heterogeneity of daily routines that moderate behavior (e.g., play, feeding, errands) \autocite{KadookaCaufield2021,Tamis-LeMondaCustode2018}. ``Burstiness'' of behavior means that long recordings are needed to capture clusters of events amid long periods in which they may be absent \autocite{BarbaroFausey2022,WarlaumontSobowale2021}. Fifth, \emph{automatic classification} means that the approach can scale to analyze large numbers of participants over long recordings without the bottleneck of manual annotation/transcription.

But automatic classification can only replace human annotation if it is sufficiently accurate and unbiased. An independent assessment of the LENA® algorithms found mixed results about the accuracy of different measurements. For example, correlations between human transcribed counts of adult words and child vocalizations against LENA®'s automatic counts were strong, \emph{r} = .698 and \emph{r} = .649, respectively \autocite{CristiaLavechin2020}. For other metrics, such as the number of ``conversational turns'' between the child and communicative partners, agreement was poor (\emph{r} = .364). Thus, for some use cases (and for some metrics), long form audio recordings provide a mobile, unobtrusive way to automatically score real-time data over a full day. In the remainder of the paper, we turn to the question of how to replicate those key features in long form recordings of motor behavior.

@@

Video and survey methods are the current state-of-the-art in assessing infants' gross motor behavior in naturalistic tasks. Although each method has complementary advantages and disadvantages for characterizing infants' everyday motor experiences, neither method on its own can provide comparable data to the long form audio recordings reviewed in the previous section.

Video observation is the most common way of measuring infant motor behavior in home recordings. Most often, an experimenter with a handheld camera follows infants from room to room to ensure that their movements are visible throughout the recording session \autocite{Karasik2011,ChenSchneider2022,HerzbergFletcher2021}. The primary advantage of video recording is that it captures real-time behavior. Infants' body position, locomotion, and reaching comprise events that occur on the timescale of seconds, so standard video recording is adequate to score gross motor behavior. However, requiring an experimenter to operate a camera is obtrusive, whereas relying on a stationary camera means that infants will be absent from view as they move from place to place. Moreover, video observation cannot easily scale to long durations or large numbers of participants. Logistically, an experimenter cannot follow behind infants to record their behavior from morning to night (and were they to do so, they would likely alter infants' and caregivers' behavior). Typical video recording sessions last 45-120 minutes \autocite{Karasik2011,ChenSchneider2022,HerzbergFletcher2021}, far short of capturing the variety of activities across the full daily routine. Even if full day videos were available, the lack of suitable automatic classification tools means that the human cost of annotation makes it difficult for video methods to scale to testing large numbers of participants. Our annotation of body position takes approximately 2-5 hours to complete for every hour of video (depending on how often infants switch positions), meaning that a full ``waking day'' of approximately 11 hours for a 12-month-old \autocite{GallandTaylor2012} could take 22-55 hours of labor to fully annotate.

In contrast, survey methods such as daily diaries/inventories or ecological momentary assessment (EMA) are mobile, unobtrusive, can be applied across an entire day, and do not need laborious annotation. Diary studies provide caregivers with logs or structured interviews to estimate from memory how much time infants spend in particular activities \autocite{MajnemerBarr2005,KarasikKuchirko2022}. Ecological momentary assessment uses text-message or app-based notifications to prompt caregivers to make repeated estimates of infants' behavior over the course of a day \autocite{Survey,KadookaCaufield2021}. Although the EMA responses are valuable in aggregate, survey methods lack the real-time temporal resolution to describe moment-to-moment changes in behavior. For diaries and interviews, limits on caregivers' memory mean that they will report what was most frequent, but cannot remember events that happen on the scale of seconds and minutes. At best, EMA surveys prompt caregivers to make hourly observations; increasing the number of surveys per day would be too burdensome for the respondent. Thus, despite being a useful tool for estimating broad developmental changes and individual differences in infants' motor experiences, survey methods are not suited for capturing within-participant temporal dynamics.

>>>>

Infants' movements facilitate and constrain how they can interact with their surroundings. Changes in \emph{body position}---whether infants are supine on their backs, prone on their bellies, sitting, upright, or held by a caregiver---have in-the-moment consequences for vision, object exploration, and social interaction. When sitting and upright, infants have a better view of faces and distant objects compared to their view while prone \autocite{Freeplay,LuoFranchak2020,CWW}. While walking upright, infants move farther away from caregivers and share toys in different ways compared to infants crawling in a prone position \autocite{ChenSchneider2022,Karasik2011}. As infants grow older and acquire new abilities, such as independent sitting and walking, they spend more time sitting and upright and less time held, supine, and prone \autocite{Survey,Thurman2017,Freeplay,AdolphCTL2014}. Thus, characterizing individual differences in the day-to-day accumulation of body position experiences informs developmental theory by revealing differential opportunities for learning \autocite{CurrentOpinion}.

In this paper, we present an inertial sensing method to classify infants' full-day, real-time body position. Our method takes inspiration from a more mature technology: Long-form audio recordings of infants' language experiences. We begin by identifying the key features of wearable audio recorders that should be replicated in long-form recordings of motor behavior. Next, we review the current state-of-the-art in measuring infant motor behavior---video and survey data---and their limitations in capturing real-time, full-day behavior. Finally, we discuss the advantages of using inertial sensing to classify motor behavior. Despite promising past results in brief, supervised sessions \autocite{FranchakScott2021,AiraksinenRasanen2020,AiraksinenGallen2022}, the current investigation takes a needed step forward by testing accuracy over long, unsupervised recordings in what we term a \emph{distal comparison}.

@@

The LENA® recorder is a commercial device worn in a custom shirt pocket; the recorder has sufficient battery life and storage to record for an entire day. Closed-source LENA® algorithms analyze the audio recordings to provide automatic counts of useful metrics, such as the number of words spoken by adults in the vicinity of the infant. Long-form audio recordings have had a transformational impact on language development research by allowing researchers to characterize opportunities for learning in daily life. For example, measuring the amount of speech heard by infants in the home \autocite{Weisleder2013} or in a daycare setting \autocite{PerryPrince2018} revealed how individual differences in speech input predict later vocabulary. Full-day language recording synchronized with other data sources allows researchers to identify how auditory input and vocal production interact with other processes. Beyond individual differences in aggregated data, long-form recordings reveal the temporal schedule of experiences. For example, infants' daily experiences hearing music are clustered in time, with ``bursty'' episodes of music presence separated by relatively long periods during which music is absent \autocite{MendozaFausey2022}.

We identified five key features of long-form audio methods that should be replicated in analogous studies of motor behavior. First, wearable audio recorders are \emph{mobile}. Measurement is not limited to a particular room because the recording device travels with the participant. Data are recorded to onboard device memory, so participants do not need to be in range of a receiver. Second, wearable audio recording is more \emph{unobtrusive}. Participants' reactivity to observation, such as from a video camera, may influence behavior more compared with a sensor that records only motion or audio data. For example, caregivers spoke more frequently to infants during a video-recorded portion of a home recording compared with audio-only segments captured by a LENA® device \autocite{Bergelson2019Input}. Third and fourth, recordings capture \emph{real-time data} over a \emph{full day}. Real-time data are vital for identifying processes that unfold over minutes or seconds within an individual as opposed to comparisons of aggregated data between infants. Synchronizing real-time data to other data streams helps to reveal sources of variability within an individual \autocites[e.g.,][]{WassPhillips2022,MalachowskiSalo2023}. Full-day recordings are essential for capturing experiences across the heterogeneity of daily routines that moderate behavior (e.g., play, feeding, errands) \autocite{KadookaCaufield2021,Tamis-LeMondaCustode2018}. ``Burstiness'' of behavior means that long recordings are needed to capture clusters of events amid long periods in which they may be absent \autocite{BarbaroFausey2022,WarlaumontSobowale2021}. Fifth, \emph{automatic classification} means that the approach can scale to analyze large numbers of participants over long recordings without the bottleneck of manual annotation/transcription.

But automatic classification can only replace human annotation if it is sufficiently accurate. An independent assessment of the LENA® algorithms found mixed results about classification accuracy. Correlations between human transcribed counts of adult words and child vocalizations against LENA®'s automatic counts were strong, \emph{r} = .698 and \emph{r} = .649, respectively \autocite{CristiaLavechin2020}. For other metrics, such as the number of ``conversational turns'' between the child and communicative partners, agreement was poor (\emph{r} = .364). Thus, for some use cases (and for some metrics), long form audio recordings provide a mobile, unobtrusive way to automatically score real-time data over a full day.

@@

Video and survey methods are the current state-of-the-art in assessing infants' gross motor behavior in naturalistic tasks. Although each method has complementary advantages and disadvantages for characterizing infants' everyday motor experiences, neither method fulfills all five key features of long form audio recordings reviewed in the previous section.

Video observation is the most common way of measuring infant motor behavior in home recordings. Most often, an experimenter with a handheld camera follows infants from room to room to ensure that their movements are visible throughout the recording session \autocite{Karasik2011,ChenSchneider2022,HerzbergFletcher2021}. The primary advantage of video recording is that it captures real-time behavior.Standard 30 Hz video recording is adequate to capture changes in infant body position that occur on the timescale of seconds. However, requiring an experimenter to operate a camera is obtrusive, whereas relying on a stationary camera means that infants will be absent from view as they move from place to place. Moreover, video observation cannot easily scale to long durations or large numbers of participants. An experimenter cannot follow behind infants to record their behavior from morning to night; typical video recording sessions last 45-120 minutes \autocite{Karasik2011,ChenSchneider2022,HerzbergFletcher2021}, far short of capturing the variety of activities across the full daily routine. Even if full-day videos were available, the lack of suitable automatic classification tools means that the human cost of annotation would be immense. Our annotation of body position takes approximately 2-5 hours to complete for every hour of video (depending on how often infants switch positions), meaning that a full ``waking day'' of approximately 11 hours for a 12-month-old \autocite{GallandTaylor2012} could take 22-55 hours of labor to annotate.

In contrast, survey methods such as daily diaries/inventories or ecological momentary assessment (EMA) are mobile, unobtrusive, can be applied across an entire day, and do not need laborious annotation. Diary studies provide caregivers with logs or structured interviews record activities \autocite{MajnemerBarr2005,KarasikKuchirko2022}. Ecological momentary assessment uses smartphone notifications to prompt caregivers to make repeated estimates of behaviors throughout the day \autocite{Survey,KadookaCaufield2021}. Although such survey responses are valuable in aggregate, they lack the real-time temporal resolution to describe moment-to-moment changes in behavior. At best, EMA surveys prompt caregivers to make hourly observations; increasing the number of surveys per day would be too burdensome for the respondent. Thus, despite being a useful tool for estimating broad developmental changes and individual differences in infants' motor experiences, survey methods are not suited for capturing within-participant temporal dynamics.
